DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
reviewed conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The \tool can automatically synthesize stable and safe digital controllers for intricate dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space equation using CEGIS. 
In particular, the \tool represents the first fully automated synthesis
tool that is algorithmically and numerically sound, considering various error
sources in the implementation of the digital control algorithm and in the computational 
modeling of plant dynamics~\cite{abate2017,abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its 
digital implementation. 
%
As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).

>>>>

The \tool can automatically synthesize stable and safe digital controllers for intricate dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space equation using CEGIS. 
In particular, the \tool represents the first fully automated synthesis
tool that is algorithmically and numerically sound, considering various error
sources in the implementation of the digital control algorithm and in the computational 
modeling of plant dynamics~\cite{abate2017,abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable and safe digital controllers for physical plants, while taking into account all aspects of its 
digital implementation. 
%
As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties.
